How do changes in ex vary between countries?

### 2022-03-08 draft_paper.Rmd
did the gridsearch approach - seem to be more sensible answers!

anova(null_alt_model, best_alt_model)

@@

>>>>

@@

# There are two alternative approaches:

# 1) Use an exhaustive grid search approach 
# 2) Use an algorithm which is less likely to get stuck in local optima

# The first approach is much more sensible, but the second might be a cool
# stretch goal as well!

# let's use a heavily modified version of the above function to do the grid search

get_best_tau_from_gridsearch <- function(df, buffer = 2, what = c("best", "all")){
  # We can put in some data validation checks too

  years <- df$year 
  tau_lower <- min(years) + buffer # the lower bound 
  tau_upper <- max(years) - buffer # the upper bound
  tau_searchrange <- tau_lower:tau_upper

  get_result_from_model <- function(tau, df, what = c("AIC", "BIC", "model")){
    # Again, can carry out more validation checks 
    what <- match.arg(what)

  search_df <- tibble(
    tau = tau_searchrange
  ) %>% 
    mutate(aic = map_dbl(tau, get_result_from_model, df = df))

  if (what == "all") {return(search_df)}

  if (what == "best") {
    out <- 
      search_df %>% 
        filter(aic == min(aic)) %>% 
        pull(tau)
    return(out)
  }

hmd_ex_selected_countries_with_synth %>%
  filter(year >= 1979) %>% 
  group_by(code, x, sex) %>% 
  nest() %>% 
  mutate(
    best_tau = map_dbl(data, get_best_tau_from_gridsearch)
  )
